---
title: "social_commerce_content_perceptions_analysis"
author: "Eliana"
date: "2026-09-18"
output: word_document
---
# 0. Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
library(ggplot2)
library(tidyr)
library(psych)
library(effectsize)

options(scipen = 999)

d_raw <- read_csv('../data/01_raw_final_data.csv')
```
# 1. Research Questions and Hypotheses

## Main Research Question
How do commercial visibility and information diagnosticity influence Content Trust in creator-led social commerce?

## Sub-Research Question 1
Does persuasion knowledge awareness mediate the relationship between commercial visibility and Content Trust, and is this indirect relationship moderated by information diagnosticity?

## Sub-Research Question 2
Do commercial visibility and information diagnosticity affect Content Trust and Platform Trust differently?

## Hypotheses
H1: Higher CV will lead to lower Content Trust.

H2: Higher ID will lead to higher Content Trust.

H3: The negative effect of CV on Content Trust will be mediated by PKA.

H4: ID will moderate the indirect effect of CV on Content Trust via PKA, such that the negative indirect effect will be weaker when ID is high.

# 2. Raw Data Overview
```{r}
dim(d_raw)
names(d_raw)
d_raw %>%
  select(
    StartDate,
    Status,
    Progress,
    Finished,
    ResponseId,
    DistributionChannel,
    Condition
  ) %>%
  head(5)
```
# 3. Data Screening and Final Analytical Sample
```{r}
# Remove Qualtrics metadata rows and survey previews
d_formal <- d_raw %>%
  filter(
    Status != "Survey Preview",
    Status != "Response Type",
    !grepl("ImportId", Status, fixed = TRUE)
  )

# Retain completed responses
d_complete <- d_formal %>%
  filter(
    Progress == 100,
    Finished == TRUE
  )

# Apply consent and eligibility criteria
d_eligible <- d_complete %>%
  filter(
     `Consent Form` == "I agree",
    S1 == "Yes",
    S2 == "Yes",
    S3 != "I don't use social media",
    S4 == "Yes"
  )

# Apply attention-check criterion
d_clean <- d_eligible %>%
  filter(
    `Attention Check` == "Strongly agree"
    )

# Screening summary
screening_summary <- data.frame(
  Stage = c(
    "Formal responses",
    "Completed responses",
    "Eligible responses",
    "Final analytical sample"
  ),
  N = c(
    nrow(d_formal),
    nrow(d_complete),
    nrow(d_eligible),
    nrow(d_clean)
  )
)

screening_summary

# Final condition allocation
d_clean %>%
  count(Condition)
```
A total of 298 formal responses were identified, all of which were complete. Eligibility screening retained 277 responses, and 246 responses remained after application of the attention-check criterion. The final sample was approximately balanced across the four experimental conditions: HH (n = 62), HL (n = 63), LH (n = 60), and LL (n = 61).

# 4. Variable Coding and Scale Construction
```{r}
# Convert agreement-scale responses to numeric values
likert_to_num <- function(x) {
  recode(
    x,
    "Strongly disagree" = 1,
    "Disagree" = 2,
    "Somewhat disagree" = 3,
    "Neither agree nor disagree" = 4,
    "Somewhat agree" = 5,
    "Agree" = 6,
    "Strongly agree" = 7
  )
}

# Create analysis-ready variables
d_analysis <- d_clean %>%
  rename(
    MC_CV1 = `MC-CV1`,
    MC_CV2 = `MC-CV2`,
    MC_ID1 = `MC-ID1`,
    MC_ID2 = `MC-ID2`,
    MC_ID3 = `MC-ID3`,
    AgeGroup = `DEM 1`,
    Gender = `DEM 2`,
    PriorPurchase = `DEM 3`,
    Familiarity = `DEM 4`
  ) %>%
  mutate(
    across(
      c(
        CT1, CT2, CT3, CT4,
        PT1, PT2, PT3, PT4,
        PKA1, PKA2, PKA3, PKA4,
        MC_CV1, MC_CV2,
        MC_ID1, MC_ID2, MC_ID3
      ),
      likert_to_num
    ),

    Familiarity = recode(
      Familiarity,
      "Not familiar at all" = 1,
      "Slightly familiar" = 2,
      "Somewhat familiar" = 3,
      "Moderately familiar" = 4,
      "Quite familiar" = 5,
      "Very familiar" = 6,
      "Extremely familiar" = 7
    ),

    CV_num = ifelse(Condition %in% c("HH", "HL"), 1, 0),
    ID_num = ifelse(Condition %in% c("HH", "LH"), 1, 0),

    CV = factor(
      CV_num,
      levels = c(0, 1),
      labels = c("Low", "High")
    ),

    ID = factor(
      ID_num,
      levels = c(0, 1),
      labels = c("Low", "High")
    ),

    Condition = factor(
      Condition,
      levels = c("LL", "LH", "HL", "HH")
    ),

    AgeGroup = factor(
      AgeGroup,
      levels = c(
        "18-24",
        "25-34",
        "35-44",
        "45 or above",
        "Prefer not to say"
      )
    ),

    Gender = factor(Gender),
    PriorPurchase = factor(PriorPurchase),

    CT = rowMeans(cbind(CT1, CT2, CT3, CT4)),
    PT = rowMeans(cbind(PT1, PT2, PT3, PT4)),
    PKA = rowMeans(cbind(PKA1, PKA2, PKA3, PKA4)),
    CV_check = rowMeans(cbind(MC_CV1, MC_CV2)),
    ID_check = rowMeans(cbind(MC_ID1, MC_ID2, MC_ID3)),

    # Mean-centred mediator for moderated mediation
    PKA_c = PKA - mean(PKA, na.rm = TRUE)
  )

write_csv(
  d_analysis,
  "../data/02_Cleaned_Analytical_Data.csv"
)
```