---
title: "social_commerce_content_perceptions_analysis"
author: "Eliana"
date: "2026-09-18"
output: word_document
---
# 0. Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
library(ggplot2)
library(tidyr)
library(psych)
library(effectsize)

options(scipen = 999)

d_raw <- read_csv('../data/01_raw_final_data.csv')
```
# 1. Research Questions and Hypotheses

## Main Research Question
How do commercial visibility and information diagnosticity influence Content Trust in creator-led social commerce?

## Sub-Research Question 1
Does persuasion knowledge awareness mediate the relationship between commercial visibility and Content Trust, and is this indirect relationship moderated by information diagnosticity?

## Sub-Research Question 2
Do commercial visibility and information diagnosticity affect Content Trust and Platform Trust differently?

## Hypotheses
H1: Higher CV will lead to lower Content Trust.

H2: Higher ID will lead to higher Content Trust.

H3: The negative effect of CV on Content Trust will be mediated by PKA.

H4: ID will moderate the indirect effect of CV on Content Trust via PKA, such that the negative indirect effect will be weaker when ID is high.

# 2. Raw Data Overview
```{r}
dim(d_raw)
names(d_raw)
d_raw %>%
  select(
    StartDate,
    Status,
    Progress,
    Finished,
    ResponseId,
    DistributionChannel,
    Condition
  ) %>%
  head(5)
```
# 3. Data Screening and Final Analytical Sample
```{r}
# Remove Qualtrics metadata rows and survey previews
d_formal <- d_raw %>%
  filter(
    Status != "Survey Preview",
    Status != "Response Type",
    !grepl("ImportId", Status, fixed = TRUE)
  )

# Retain completed responses
d_complete <- d_formal %>%
  filter(
    Progress == 100,
    Finished == TRUE
  )

# Apply consent and eligibility criteria
d_eligible <- d_complete %>%
  filter(
     `Consent Form` == "I agree",
    S1 == "Yes",
    S2 == "Yes",
    S3 != "I don't use social media",
    S4 == "Yes"
  )

# Apply attention-check criterion
d_clean <- d_eligible %>%
  filter(
    `Attention Check` == "Strongly agree"
    )

# Screening summary
screening_summary <- data.frame(
  Stage = c(
    "Formal responses",
    "Completed responses",
    "Eligible responses",
    "Final analytical sample"
  ),
  N = c(
    nrow(d_formal),
    nrow(d_complete),
    nrow(d_eligible),
    nrow(d_clean)
  )
)

screening_summary

# Final condition allocation
d_clean %>%
  count(Condition)
```
A total of 298 formal responses were identified, all of which were complete. Eligibility screening retained 277 responses, and 246 responses remained after application of the attention-check criterion. The final sample was approximately balanced across the four experimental conditions: HH (n = 62), HL (n = 63), LH (n = 60), and LL (n = 61).

# 4. Variable Coding and Scale Construction
```{r}
# Convert agreement-scale responses to numeric values
likert_to_num <- function(x) {
  recode(
    x,
    "Strongly disagree" = 1,
    "Disagree" = 2,
    "Somewhat disagree" = 3,
    "Neither agree nor disagree" = 4,
    "Somewhat agree" = 5,
    "Agree" = 6,
    "Strongly agree" = 7
  )
}

# Create analysis-ready variables
d_analysis <- d_clean %>%
  rename(
    MC_CV1 = `MC-CV1`,
    MC_CV2 = `MC-CV2`,
    MC_ID1 = `MC-ID1`,
    MC_ID2 = `MC-ID2`,
    MC_ID3 = `MC-ID3`,
    AgeGroup = `DEM 1`,
    Gender = `DEM 2`,
    PriorPurchase = `DEM 3`,
    Familiarity = `DEM 4`
  ) %>%
  mutate(
    across(
      c(
        CT1, CT2, CT3, CT4,
        PT1, PT2, PT3, PT4,
        PKA1, PKA2, PKA3, PKA4,
        MC_CV1, MC_CV2,
        MC_ID1, MC_ID2, MC_ID3
      ),
      likert_to_num
    ),

    Familiarity = recode(
      Familiarity,
      "Not familiar at all" = 1,
      "Slightly familiar" = 2,
      "Somewhat familiar" = 3,
      "Moderately familiar" = 4,
      "Quite familiar" = 5,
      "Very familiar" = 6,
      "Extremely familiar" = 7
    ),

    CV_num = ifelse(Condition %in% c("HH", "HL"), 1, 0),
    ID_num = ifelse(Condition %in% c("HH", "LH"), 1, 0),

    CV = factor(
      CV_num,
      levels = c(0, 1),
      labels = c("Low", "High")
    ),

    ID = factor(
      ID_num,
      levels = c(0, 1),
      labels = c("Low", "High")
    ),

    Condition = factor(
      Condition,
      levels = c("LL", "LH", "HL", "HH")
    ),

    AgeGroup = factor(
      AgeGroup,
      levels = c(
        "18-24",
        "25-34",
        "35-44",
        "45 or above",
        "Prefer not to say"
      )
    ),

    Gender = factor(Gender),
    PriorPurchase = factor(PriorPurchase),

    CT = rowMeans(cbind(CT1, CT2, CT3, CT4)),
    PT = rowMeans(cbind(PT1, PT2, PT3, PT4)),
    PKA = rowMeans(cbind(PKA1, PKA2, PKA3, PKA4)),
    CV_check = rowMeans(cbind(MC_CV1, MC_CV2)),
    ID_check = rowMeans(cbind(MC_ID1, MC_ID2, MC_ID3)),

    # Mean-centred mediator for moderated mediation
    PKA_c = PKA - mean(PKA, na.rm = TRUE)
  )

write_csv(
  d_analysis,
  "../data/02_Cleaned_Analytical_Data.csv"
)
```
# 5. Sample Description
```{r}
# Age distribution
age_summary <- d_analysis %>%
  count(AgeGroup) %>%
  mutate(Percent = n / sum(n) * 100)

age_summary

# Gender distribution
gender_summary <- d_analysis %>%
  count(Gender) %>%
  mutate(Percent = n / sum(n) * 100)

gender_summary

# Previous purchase following creator recommendations
purchase_summary <- d_analysis %>%
  count(PriorPurchase) %>%
  mutate(Percent = n / sum(n) * 100)

purchase_summary

# Facial moisturiser familiarity
familiarity_summary <- d_analysis %>%
  summarise(
    N = sum(!is.na(Familiarity)),
    Mean = mean(Familiarity, na.rm = TRUE),
    SD = sd(Familiarity, na.rm = TRUE),
    Median = median(Familiarity, na.rm = TRUE)
  )

familiarity_summary
```
The sample was primarily aged 18–34 (68.7%) and 61.8% were women. Most participants (66.7%) had previously purchased a product following a creator or influencer recommendation. Familiarity with facial moisturiser products was moderate (M = 4.16, SD = 1.79).

# 6. Measurement Quality
```{r}
# Internal consistency reliability
alpha_CT <- psych::alpha(
  d_analysis[, c("CT1", "CT2", "CT3", "CT4")]
)

alpha_PT <- psych::alpha(
  d_analysis[, c("PT1", "PT2", "PT3", "PT4")]
)

alpha_PKA <- psych::alpha(
  d_analysis[, c("PKA1", "PKA2", "PKA3", "PKA4")]
)

alpha_CV <- psych::alpha(
  d_analysis[, c("MC_CV1", "MC_CV2")]
)

alpha_ID <- psych::alpha(
  d_analysis[, c("MC_ID1", "MC_ID2", "MC_ID3")]
)

alpha_CT$total$raw_alpha
alpha_PT$total$raw_alpha
alpha_PKA$total$raw_alpha
alpha_CV$total$raw_alpha
alpha_ID$total$raw_alpha


# Descriptive statistics for principal study variables
scale_descriptives <- d_analysis %>%
  select(CT, PT, PKA) %>%
  summarise(
    across(
      everything(),
      list(
        N = ~sum(!is.na(.)),
        M = ~mean(., na.rm = TRUE),
        SD = ~sd(., na.rm = TRUE),
        Median = ~median(., na.rm = TRUE),
        Min = ~min(., na.rm = TRUE),
        Max = ~max(., na.rm = TRUE)
      )
    )
  ) %>%
  pivot_longer(
    everything(),
    names_to = c("Variable", ".value"),
    names_pattern = "(.*)_(N|Median|Min|Max|SD|M)$"
  )

scale_descriptives

# Pearson correlations with significance tests
cor_results <- psych::corr.test(
  d_analysis[, c("CT", "PT", "PKA")],
  use = "pairwise",
  method = "pearson",
  adjust = "none"
)

round(cor_results$r, 2)
round(cor_results$p, 3)
```
All multi-item measures showed strong internal consistency, with Cronbach’s α ranging from .882 to .937. Content Trust averaged 4.27 (SD = 1.62), Platform Trust 3.92 (SD = 1.57), and Persuasion Knowledge Awareness 6.18 (SD = 1.08). Content Trust was positively associated with Platform Trust, r = .62, p < .001, but was not significantly associated with PKA, r = .07, p = .257. Platform Trust showed a weak positive association with PKA, r = .13, p = .048.

# 7. Manipulation Checks
```{r}
# Descriptive statistics by experimental condition
manipulation_descriptives <- d_analysis %>%
  group_by(CV, ID) %>%
  summarise(
    n = n(),
    CV_check_M = mean(CV_check),
    CV_check_SD = sd(CV_check),
    ID_check_M = mean(ID_check),
    ID_check_SD = sd(ID_check),
    .groups = "drop"
  )

manipulation_descriptives

# Commercial Visibility manipulation check
cv_check_model <- aov(
  CV_check ~ CV * ID, 
  data = d_analysis
  )

summary(cv_check_model)

# Information Diagnosticity manipulation check
id_check_model <- aov(
  ID_check ~ CV * ID, 
  data = d_analysis
  )

summary(id_check_model)

# ANOVA effect sizes
eta_squared(
  cv_check_model,
  partial = TRUE
)

eta_squared(
  id_check_model,
  partial = TRUE
)

# Descriptive effect sizes for target manipulations
cohens_d(
  CV_check ~ CV, 
  data = d_analysis
  )

cohens_d(
  ID_check ~ ID, 
  data = d_analysis
  )
```
Both manipulations were successful. High CV produced higher perceived commercial visibility than low CV, F(1, 242) = 29.50, p < .001, ηₚ² = .11, |d| = 0.69. High ID produced higher perceived information diagnosticity than low ID, F(1, 242) = 61.55, p < .001, ηₚ² = .20, |d| = 1.00. Neither manipulation showed a significant main effect on the non-target manipulation check, and neither CV × ID interaction was significant.