---
title: "social_commerce_content_perceptions_analysis"
author: "Eliana"
date: "2026-09-18"
output: word_document
---
# 0. Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
library(ggplot2)
library(tidyr)
library(psych)
library(effectsize)

options(scipen = 999)

d_raw <- read_csv('../data/01_raw_final_data.csv')
```
# 1. Research Questions and Hypotheses

## Main Research Question
How do commercial visibility and information diagnosticity influence Content Trust in creator-led social commerce?

## Sub-Research Question 1
Does persuasion knowledge awareness mediate the relationship between commercial visibility and Content Trust, and is this indirect relationship moderated by information diagnosticity?

## Sub-Research Question 2
Do commercial visibility and information diagnosticity affect Content Trust and Platform Trust differently?

## Hypotheses
H1: Higher CV will lead to lower Content Trust.

H2: Higher ID will lead to higher Content Trust.

H3: The negative effect of CV on Content Trust will be mediated by PKA.

H4: ID will moderate the indirect effect of CV on Content Trust via PKA, such that the negative indirect effect will be weaker when ID is high.

# 2. Raw Data Overview
```{r}
dim(d_raw)
names(d_raw)
d_raw %>%
  select(
    StartDate,
    Status,
    Progress,
    Finished,
    ResponseId,
    DistributionChannel,
    Condition
  ) %>%
  head(5)
```
# 3. Data Screening and Final Analytical Sample
```{r}
# Remove Qualtrics metadata rows and survey previews
d_formal <- d_raw %>%
  filter(
    Status != "Survey Preview",
    Status != "Response Type",
    !grepl("ImportId", Status, fixed = TRUE)
  )

# Retain completed responses
d_complete <- d_formal %>%
  filter(
    Progress == 100,
    Finished == TRUE
  )

# Apply consent and eligibility criteria
d_eligible <- d_complete %>%
  filter(
     `Consent Form` == "I agree",
    S1 == "Yes",
    S2 == "Yes",
    S3 != "I don't use social media",
    S4 == "Yes"
  )

# Apply attention-check criterion
d_clean <- d_eligible %>%
  filter(
    `Attention Check` == "Strongly agree"
    )

# Screening summary
screening_summary <- data.frame(
  Stage = c(
    "Formal responses",
    "Completed responses",
    "Eligible responses",
    "Final analytical sample"
  ),
  N = c(
    nrow(d_formal),
    nrow(d_complete),
    nrow(d_eligible),
    nrow(d_clean)
  )
)

screening_summary

# Final condition allocation
d_clean %>%
  count(Condition)
```
A total of 298 formal responses were identified, all of which were complete. Eligibility screening retained 277 responses, and 246 responses remained after application of the attention-check criterion. The final sample was approximately balanced across the four experimental conditions: HH (n = 62), HL (n = 63), LH (n = 60), and LL (n = 61).

# 4. Variable Coding and Scale Construction
```{r}
# Convert agreement-scale responses to numeric values
likert_to_num <- function(x) {
  recode(
    x,
    "Strongly disagree" = 1,
    "Disagree" = 2,
    "Somewhat disagree" = 3,
    "Neither agree nor disagree" = 4,
    "Somewhat agree" = 5,
    "Agree" = 6,
    "Strongly agree" = 7
  )
}

# Create analysis-ready variables
d_analysis <- d_clean %>%
  rename(
    MC_CV1 = `MC-CV1`,
    MC_CV2 = `MC-CV2`,
    MC_ID1 = `MC-ID1`,
    MC_ID2 = `MC-ID2`,
    MC_ID3 = `MC-ID3`,
    AgeGroup = `DEM 1`,
    Gender = `DEM 2`,
    PriorPurchase = `DEM 3`,
    Familiarity = `DEM 4`
  ) %>%
  mutate(
    across(
      c(
        CT1, CT2, CT3, CT4,
        PT1, PT2, PT3, PT4,
        PKA1, PKA2, PKA3, PKA4,
        MC_CV1, MC_CV2,
        MC_ID1, MC_ID2, MC_ID3
      ),
      likert_to_num
    ),

    Familiarity = recode(
      Familiarity,
      "Not familiar at all" = 1,
      "Slightly familiar" = 2,
      "Somewhat familiar" = 3,
      "Moderately familiar" = 4,
      "Quite familiar" = 5,
      "Very familiar" = 6,
      "Extremely familiar" = 7
    ),

    CV_num = ifelse(Condition %in% c("HH", "HL"), 1, 0),
    ID_num = ifelse(Condition %in% c("HH", "LH"), 1, 0),

    CV = factor(
      CV_num,
      levels = c(0, 1),
      labels = c("Low", "High")
    ),

    ID = factor(
      ID_num,
      levels = c(0, 1),
      labels = c("Low", "High")
    ),

    Condition = factor(
      Condition,
      levels = c("LL", "LH", "HL", "HH")
    ),

    AgeGroup = factor(
      AgeGroup,
      levels = c(
        "18-24",
        "25-34",
        "35-44",
        "45 or above",
        "Prefer not to say"
      )
    ),

    Gender = factor(Gender),
    PriorPurchase = factor(PriorPurchase),

    CT = rowMeans(cbind(CT1, CT2, CT3, CT4)),
    PT = rowMeans(cbind(PT1, PT2, PT3, PT4)),
    PKA = rowMeans(cbind(PKA1, PKA2, PKA3, PKA4)),
    CV_check = rowMeans(cbind(MC_CV1, MC_CV2)),
    ID_check = rowMeans(cbind(MC_ID1, MC_ID2, MC_ID3)),

    # Mean-centred mediator for moderated mediation
    PKA_c = PKA - mean(PKA, na.rm = TRUE)
  )

write_csv(
  d_analysis,
  "../data/02_Cleaned_Analytical_Data.csv"
)
```
# 5. Sample Description
```{r}
# Age distribution
age_summary <- d_analysis %>%
  count(AgeGroup) %>%
  mutate(Percent = n / sum(n) * 100)

age_summary

# Gender distribution
gender_summary <- d_analysis %>%
  count(Gender) %>%
  mutate(Percent = n / sum(n) * 100)

gender_summary

# Previous purchase following creator recommendations
purchase_summary <- d_analysis %>%
  count(PriorPurchase) %>%
  mutate(Percent = n / sum(n) * 100)

purchase_summary

# Facial moisturiser familiarity
familiarity_summary <- d_analysis %>%
  summarise(
    N = sum(!is.na(Familiarity)),
    Mean = mean(Familiarity, na.rm = TRUE),
    SD = sd(Familiarity, na.rm = TRUE),
    Median = median(Familiarity, na.rm = TRUE)
  )

familiarity_summary
```
The sample was primarily aged 18–34 (68.7%) and 61.8% were women. Most participants (66.7%) had previously purchased a product following a creator or influencer recommendation. Familiarity with facial moisturiser products was moderate (M = 4.16, SD = 1.79).

# 6. Measurement Quality
```{r}
# Internal consistency reliability
alpha_CT <- psych::alpha(
  d_analysis[, c("CT1", "CT2", "CT3", "CT4")]
)

alpha_PT <- psych::alpha(
  d_analysis[, c("PT1", "PT2", "PT3", "PT4")]
)

alpha_PKA <- psych::alpha(
  d_analysis[, c("PKA1", "PKA2", "PKA3", "PKA4")]
)

alpha_CV <- psych::alpha(
  d_analysis[, c("MC_CV1", "MC_CV2")]
)

alpha_ID <- psych::alpha(
  d_analysis[, c("MC_ID1", "MC_ID2", "MC_ID3")]
)

alpha_CT$total$raw_alpha
alpha_PT$total$raw_alpha
alpha_PKA$total$raw_alpha
alpha_CV$total$raw_alpha
alpha_ID$total$raw_alpha


# Descriptive statistics for principal study variables
scale_descriptives <- d_analysis %>%
  select(CT, PT, PKA) %>%
  summarise(
    across(
      everything(),
      list(
        N = ~sum(!is.na(.)),
        M = ~mean(., na.rm = TRUE),
        SD = ~sd(., na.rm = TRUE),
        Median = ~median(., na.rm = TRUE),
        Min = ~min(., na.rm = TRUE),
        Max = ~max(., na.rm = TRUE)
      )
    )
  ) %>%
  pivot_longer(
    everything(),
    names_to = c("Variable", ".value"),
    names_pattern = "(.*)_(N|Median|Min|Max|SD|M)$"
  )

scale_descriptives

# Pearson correlations with significance tests
cor_results <- psych::corr.test(
  d_analysis[, c("CT", "PT", "PKA")],
  use = "pairwise",
  method = "pearson",
  adjust = "none"
)

round(cor_results$r, 2)
round(cor_results$p, 3)
```
All multi-item measures showed strong internal consistency, with Cronbach’s α ranging from .882 to .937. Content Trust averaged 4.27 (SD = 1.62), Platform Trust 3.92 (SD = 1.57), and Persuasion Knowledge Awareness 6.18 (SD = 1.08). Content Trust was positively associated with Platform Trust, r = .62, p < .001, but was not significantly associated with PKA, r = .07, p = .257. Platform Trust showed a weak positive association with PKA, r = .13, p = .048.

# 7. Manipulation Checks
```{r}
# Descriptive statistics by experimental condition
manipulation_descriptives <- d_analysis %>%
  group_by(CV, ID) %>%
  summarise(
    n = n(),
    CV_check_M = mean(CV_check),
    CV_check_SD = sd(CV_check),
    ID_check_M = mean(ID_check),
    ID_check_SD = sd(ID_check),
    .groups = "drop"
  )

manipulation_descriptives

# Commercial Visibility manipulation check
cv_check_model <- aov(
  CV_check ~ CV * ID, 
  data = d_analysis
  )

summary(cv_check_model)

# Information Diagnosticity manipulation check
id_check_model <- aov(
  ID_check ~ CV * ID, 
  data = d_analysis
  )

summary(id_check_model)

# ANOVA effect sizes
eta_squared(
  cv_check_model,
  partial = TRUE
)

eta_squared(
  id_check_model,
  partial = TRUE
)

# Descriptive effect sizes for target manipulations
cohens_d(
  CV_check ~ CV, 
  data = d_analysis
  )

cohens_d(
  ID_check ~ ID, 
  data = d_analysis
  )
```
Both manipulations were successful. High CV produced higher perceived commercial visibility than low CV, F(1, 242) = 29.50, p < .001, ηₚ² = .11, |d| = 0.69. High ID produced higher perceived information diagnosticity than low ID, F(1, 242) = 61.55, p < .001, ηₚ² = .20, |d| = 1.00. Neither manipulation showed a significant main effect on the non-target manipulation check, and neither CV × ID interaction was significant.

# 8. Findings

## 8.1 H1 and H2: Factorial Effects on Content Trust
```{r}
# Two-way ANOVA for Content Trust
ct_model <- aov(
  CT ~ CV * ID, 
  data = d_analysis
  )

summary(ct_model)

# Content Trust by experimental condition
ct_descriptives <- d_analysis %>%
  group_by(CV, ID) %>%
  summarise(
    n = n(),
    M = mean(CT),
    SD = sd(CT),
    .groups = "drop"
  )

ct_descriptives

# Effect sizes for Content Trust ANOVA
eta_squared(
  ct_model,
  partial = TRUE
)

# Model diagnostics
qqnorm(residuals(ct_model))
qqline(residuals(ct_model))

fligner.test(
  CT ~ Condition,
  data = d_analysis
)
```
Residuals showed close alignment with the expected distribution across the central range, with modest tail deviations. The Fligner–Killeen test indicated homogeneous variances across experimental conditions, χ²(3) = 1.48, p = .687.

H1 was not supported. Commercial visibility had no significant effect on Content Trust, F(1, 242) = 0.09, p = .769, ηₚ² < .001. Mean Content Trust was similar under low CV (M = 4.24) and high CV (M = 4.30).

H2 was supported. Information diagnosticity had a significant positive effect on Content Trust, F(1, 242) = 23.60, p < .001, ηₚ² = .09. Content Trust was higher under high ID (M = 4.76) than low ID (M = 3.80).

The CV × ID interaction was not significant, F(1, 242) = 0.04, p = .841, ηₚ² < .001, indicating that the effect of Commercial Visibility on Content Trust did not differ significantly between low- and high-ID conditions.

```{r}
# Figure 1: Content Trust by CV and ID
ct_plot_data <- d_analysis %>%
  group_by(CV, ID) %>%
  summarise(
    M = mean(CT),
    SE = sd(CT) / sqrt(n()),
    .groups = "drop"
  )

ggplot(
  ct_plot_data,
  aes(
    x = ID,
    y = M,
    group = CV,
    linetype = CV,
    shape = CV
  )
) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 3) +
  geom_errorbar(
    aes(
      ymin = M - SE,
      ymax = M + SE
    ),
    width = 0.08
  ) +
  labs(
    title = "Content Trust Across Experimental Conditions",
    x = "Information Diagnosticity",
    y = "Mean Content Trust",
    linetype = "Commercial Visibility",
    shape = "Commercial Visibility"
  ) +
  ylim(1, 7) +
  theme_minimal()
```
## 8.2 H3: Mediation via Persuasion Knowledge Awareness
```{r}
# Mediator model: effect of CV on PKA
pka_model <- lm(
  PKA ~ CV, 
  data = d_analysis
  )

summary(pka_model)

# Descriptive statistics for PKA by Commercial Visibility
pka_descriptives <- d_analysis %>%
  group_by(CV) %>%
  summarise(
    n = n(),
    M = mean(PKA, na.rm = TRUE),
    SD = sd(PKA, na.rm = TRUE),
    Median = median(PKA, na.rm = TRUE),
    .groups = "drop"
  )

pka_descriptives

# Outcome model: effects of CV, ID and PKA on Content Trust
ct_mediation_model <- lm(
  CT ~ CV + ID + PKA,
  data = d_analysis
)

summary(ct_mediation_model)

# Outcome-model diagnostics
plot(
  ct_mediation_model,
  which = 1
)

plot(
  ct_mediation_model,
  which = 2
)

plot(
  ct_mediation_model,
  which = 4
)

# Original-sample indirect effect
a_h3 <- coef(pka_model)["CVHigh"]
b_h3 <- coef(ct_mediation_model)["PKA"]

h3_indirect_original <- a_h3 * b_h3

h3_indirect_original

# Bootstrap function for H3 indirect effect
bootstrap_h3 <- function(data) {
  
  sample_data <- data[
    sample(nrow(data), replace = TRUE),
  ]
  
  a_model <- lm(
    PKA ~ CV,
    data = sample_data
  )
  
  b_model <- lm(
    CT ~ CV + ID + PKA,
    data = sample_data
  )
  
  a <- coef(a_model)["CVHigh"]
  b <- coef(b_model)["PKA"]
  
  c(
    indirect_effect = a * b
  )
}

# Bootstrap indirect effect
set.seed(123)

bootstrap_h3_results <- replicate(
  5000,
  bootstrap_h3(d_analysis)
)

bootstrap_h3_results <- as.numeric(bootstrap_h3_results)

# Original-sample estimate with bootstrap 95% confidence interval
h3_bootstrap_summary <- data.frame(
  indirect_effect = h3_indirect_original,
  lower_95 = quantile(
    bootstrap_h3_results,
    0.025,
    na.rm = TRUE
  ),
  upper_95 = quantile(
    bootstrap_h3_results,
    0.975,
    na.rm = TRUE
  )
)

h3_bootstrap_summary
```
Diagnostic plots indicated no substantial systematic pattern in the residuals. The Q–Q plot showed close alignment across the central distribution with some deviation in the tails, while Cook’s distances indicated no observations with undue influence on the outcome model.

H3 was not supported. Persuasion Knowledge Awareness averaged 6.01 (SD = 1.24) under low CV and 6.34 (SD = 0.88) under high CV. Higher commercial visibility significantly increased PKA, B = 0.33, SE = 0.14, t(244) = 2.41, p = .017. However, PKA did not significantly predict Content Trust when CV and ID were included in the outcome model, B = 0.08, SE = 0.09, t(242) = 0.91, p = .363. The indirect effect of CV on Content Trust through PKA was not significant, B = 0.028, 95% CI [-0.029, 0.106].