---
title: "social_commerce_content_perceptions_analysis"
author: "Eliana"
date: "2026-09-18"
output: word_document
---
# 0. Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
library(ggplot2)
library(tidyr)
library(psych)
library(effectsize)

options(scipen = 999)

d_raw <- read_csv('../data/01_raw_final_data.csv')
```
# 1. Research Questions and Hypotheses

## Main Research Question
How do Commercial Visibility and Information Diagnosticity influence Content Trust in creator-led social commerce?

## Sub-Research Question 1
Does Persuasion Knowledge Awareness mediate the relationship between Commercial Visibility and Content Trust, and is this indirect relationship moderated by Information Diagnosticity?

## Sub-Research Question 2
Do Commercial Visibility and Information Diagnosticity affect Content Trust and Platform Trust differently?

## Hypotheses
H1: Higher Commercial Visibility will lead to lower Content Trust.

H2: Higher Information Diagnosticity will lead to higher Content Trust.

H3: The negative effect of Commercial Visibility on Content Trust will be mediated by Persuasion Knowledge Awareness.

H4: Information Diagnosticity will moderate the indirect effect of Commercial Visibility on Content Trust through Persuasion Knowledge Awareness, such that the negative indirect effect will be weaker when Information Diagnosticity is high.

# 2. Raw Data Overview
```{r}
dim(d_raw)
names(d_raw)
d_raw %>%
  select(
    StartDate,
    Status,
    Progress,
    Finished,
    ResponseId,
    DistributionChannel,
    Condition
  ) %>%
  head(5)
```
# 3. Data Screening and Final Analytical Sample
```{r}
# Remove Qualtrics metadata rows and survey previews
d_formal <- d_raw %>%
  filter(
    Status != "Survey Preview",
    Status != "Response Type",
    !grepl("ImportId", Status, fixed = TRUE)
  )

# Retain completed responses
d_complete <- d_formal %>%
  filter(
    Progress == 100,
    Finished == TRUE
  )

# Apply consent and eligibility criteria
d_eligible <- d_complete %>%
  filter(
     `Consent Form` == "I agree",
    S1 == "Yes",
    S2 == "Yes",
    S3 != "I don't use social media",
    S4 == "Yes"
  )

# Apply attention-check criterion
d_clean <- d_eligible %>%
  filter(
    `Attention Check` == "Strongly agree"
    )

# Screening summary
screening_summary <- data.frame(
  Stage = c(
    "Formal responses",
    "Completed responses",
    "Eligible responses",
    "Final analytical sample"
  ),
  N = c(
    nrow(d_formal),
    nrow(d_complete),
    nrow(d_eligible),
    nrow(d_clean)
  )
)

screening_summary

# Final condition allocation
d_clean %>%
  count(Condition)
```
A total of 298 formal responses were identified, all of which were complete. Eligibility screening retained 277 responses, and 246 responses remained after application of the attention-check criterion. The final sample was approximately balanced across the four experimental conditions: HH (n = 62), HL (n = 63), LH (n = 60), and LL (n = 61).

# 4. Variable Coding and Scale Construction
```{r}
# Convert agreement-scale responses to numeric values
likert_to_num <- function(x) {
  recode(
    x,
    "Strongly disagree" = 1,
    "Disagree" = 2,
    "Somewhat disagree" = 3,
    "Neither agree nor disagree" = 4,
    "Somewhat agree" = 5,
    "Agree" = 6,
    "Strongly agree" = 7
  )
}

# Create analysis-ready variables
d_analysis <- d_clean %>%
  rename(
    MC_CV1 = `MC-CV1`,
    MC_CV2 = `MC-CV2`,
    MC_ID1 = `MC-ID1`,
    MC_ID2 = `MC-ID2`,
    MC_ID3 = `MC-ID3`,
    AgeGroup = `DEM 1`,
    Gender = `DEM 2`,
    PriorPurchase = `DEM 3`,
    Familiarity = `DEM 4`
  ) %>%
  mutate(
    across(
      c(
        CT1, CT2, CT3, CT4,
        PT1, PT2, PT3, PT4,
        PKA1, PKA2, PKA3, PKA4,
        MC_CV1, MC_CV2,
        MC_ID1, MC_ID2, MC_ID3
      ),
      likert_to_num
    ),

    Familiarity = recode(
      Familiarity,
      "Not familiar at all" = 1,
      "Slightly familiar" = 2,
      "Somewhat familiar" = 3,
      "Moderately familiar" = 4,
      "Quite familiar" = 5,
      "Very familiar" = 6,
      "Extremely familiar" = 7
    ),

    CV_num = ifelse(Condition %in% c("HH", "HL"), 1, 0),
    ID_num = ifelse(Condition %in% c("HH", "LH"), 1, 0),

    CV = factor(
      CV_num,
      levels = c(0, 1),
      labels = c("Low", "High")
    ),

    ID = factor(
      ID_num,
      levels = c(0, 1),
      labels = c("Low", "High")
    ),

    Condition = factor(
      Condition,
      levels = c("LL", "LH", "HL", "HH")
    ),

    AgeGroup = factor(
      AgeGroup,
      levels = c(
        "18-24",
        "25-34",
        "35-44",
        "45 or above",
        "Prefer not to say"
      )
    ),

    Gender = factor(Gender),
    PriorPurchase = factor(PriorPurchase),

    CT = rowMeans(cbind(CT1, CT2, CT3, CT4)),
    PT = rowMeans(cbind(PT1, PT2, PT3, PT4)),
    PKA = rowMeans(cbind(PKA1, PKA2, PKA3, PKA4)),
    CV_check = rowMeans(cbind(MC_CV1, MC_CV2)),
    ID_check = rowMeans(cbind(MC_ID1, MC_ID2, MC_ID3)),

    # Mean-centred mediator for moderated mediation
    PKA_c = PKA - mean(PKA, na.rm = TRUE)
  )

write_csv(
  d_analysis,
  "../data/02_Cleaned_Analytical_Data.csv"
)
```
# 5. Sample Description
```{r}
# Age distribution
age_summary <- d_analysis %>%
  count(AgeGroup) %>%
  mutate(Percent = n / sum(n) * 100)

age_summary

# Gender distribution
gender_summary <- d_analysis %>%
  count(Gender) %>%
  mutate(Percent = n / sum(n) * 100)

gender_summary

# Previous purchase following creator recommendations
purchase_summary <- d_analysis %>%
  count(PriorPurchase) %>%
  mutate(Percent = n / sum(n) * 100)

purchase_summary

# Facial moisturiser familiarity
familiarity_summary <- d_analysis %>%
  summarise(
    N = sum(!is.na(Familiarity)),
    Mean = mean(Familiarity, na.rm = TRUE),
    SD = sd(Familiarity, na.rm = TRUE),
    Median = median(Familiarity, na.rm = TRUE)
  )

familiarity_summary
```
The sample was primarily aged 18–34 (68.7%) and 61.8% were women. Most participants (66.7%) had previously purchased a product following a creator or influencer recommendation. Familiarity with facial moisturiser products was moderate (M = 4.16, SD = 1.79).

# 6. Measurement Quality
```{r}
# Internal consistency reliability
alpha_CT <- psych::alpha(
  d_analysis[, c("CT1", "CT2", "CT3", "CT4")]
)

alpha_PT <- psych::alpha(
  d_analysis[, c("PT1", "PT2", "PT3", "PT4")]
)

alpha_PKA <- psych::alpha(
  d_analysis[, c("PKA1", "PKA2", "PKA3", "PKA4")]
)

alpha_CV <- psych::alpha(
  d_analysis[, c("MC_CV1", "MC_CV2")]
)

alpha_ID <- psych::alpha(
  d_analysis[, c("MC_ID1", "MC_ID2", "MC_ID3")]
)

alpha_CT$total$raw_alpha
alpha_PT$total$raw_alpha
alpha_PKA$total$raw_alpha
alpha_CV$total$raw_alpha
alpha_ID$total$raw_alpha


# Descriptive statistics for principal study variables
scale_descriptives <- d_analysis %>%
  select(CT, PT, PKA) %>%
  summarise(
    across(
      everything(),
      list(
        N = ~sum(!is.na(.)),
        M = ~mean(., na.rm = TRUE),
        SD = ~sd(., na.rm = TRUE),
        Median = ~median(., na.rm = TRUE),
        Min = ~min(., na.rm = TRUE),
        Max = ~max(., na.rm = TRUE)
      )
    )
  ) %>%
  pivot_longer(
    everything(),
    names_to = c("Variable", ".value"),
    names_pattern = "(.*)_(N|Median|Min|Max|SD|M)$"
  )

scale_descriptives

# Pearson correlations with significance tests
cor_results <- psych::corr.test(
  d_analysis[, c("CT", "PT", "PKA")],
  use = "pairwise",
  method = "pearson",
  adjust = "none"
)

round(cor_results$r, 2)
round(cor_results$p, 3)
```
All multi-item measures showed strong internal consistency, with Cronbach’s α ranging from .882 to .937. Content Trust averaged 4.27 (SD = 1.62), Platform Trust 3.92 (SD = 1.57), and Persuasion Knowledge Awareness 6.18 (SD = 1.08). Content Trust was positively associated with Platform Trust, r = .62, p < .001, but was not significantly associated with PKA, r = .07, p = .257. Platform Trust showed a weak positive association with PKA, r = .13, p = .048.

# 7. Manipulation Checks
```{r}
# Descriptive statistics by experimental condition
manipulation_descriptives <- d_analysis %>%
  group_by(CV, ID) %>%
  summarise(
    n = n(),
    CV_check_M = mean(CV_check),
    CV_check_SD = sd(CV_check),
    ID_check_M = mean(ID_check),
    ID_check_SD = sd(ID_check),
    .groups = "drop"
  )

manipulation_descriptives

# Commercial Visibility manipulation check
cv_check_model <- aov(
  CV_check ~ CV * ID, 
  data = d_analysis
  )

summary(cv_check_model)

# Information Diagnosticity manipulation check
id_check_model <- aov(
  ID_check ~ CV * ID, 
  data = d_analysis
  )

summary(id_check_model)

# ANOVA effect sizes
eta_squared(
  cv_check_model,
  partial = TRUE
)

eta_squared(
  id_check_model,
  partial = TRUE
)

# Descriptive effect sizes for target manipulations
cohens_d(
  CV_check ~ CV, 
  data = d_analysis
  )

cohens_d(
  ID_check ~ ID, 
  data = d_analysis
  )
```
Both manipulations were successful. High CV produced higher perceived commercial visibility than low CV, F(1, 242) = 29.50, p < .001, ηₚ² = .11, |d| = 0.69. High ID produced higher perceived information diagnosticity than low ID, F(1, 242) = 61.55, p < .001, ηₚ² = .20, |d| = 1.00. Neither manipulation showed a significant main effect on the non-target manipulation check, and neither CV × ID interaction was significant.

# 8. Findings

## 8.1 H1 and H2: Factorial Effects on Content Trust
```{r}
# Two-way ANOVA for Content Trust
ct_model <- aov(
  CT ~ CV * ID, 
  data = d_analysis
  )

summary(ct_model)

# Content Trust by experimental condition
ct_descriptives <- d_analysis %>%
  group_by(CV, ID) %>%
  summarise(
    n = n(),
    M = mean(CT),
    SD = sd(CT),
    .groups = "drop"
  )

ct_descriptives

# Effect sizes for Content Trust ANOVA
eta_squared(
  ct_model,
  partial = TRUE
)

# Model diagnostics
qqnorm(residuals(ct_model))
qqline(residuals(ct_model))

fligner.test(
  CT ~ Condition,
  data = d_analysis
)
```
Residuals showed close alignment with the expected distribution across the central range, with modest tail deviations. The Fligner–Killeen test indicated homogeneous variances across experimental conditions, χ²(3) = 1.48, p = .687.

H1 was not supported. Commercial visibility had no significant effect on Content Trust, F(1, 242) = 0.09, p = .769, ηₚ² < .001. Mean Content Trust was similar under low CV (M = 4.24) and high CV (M = 4.30).

H2 was supported. Information diagnosticity had a significant positive effect on Content Trust, F(1, 242) = 23.60, p < .001, ηₚ² = .09. Content Trust was higher under high ID (M = 4.76) than low ID (M = 3.80).

The CV × ID interaction was not significant, F(1, 242) = 0.04, p = .841, ηₚ² < .001, indicating that the effect of Commercial Visibility on Content Trust did not differ significantly between low- and high-ID conditions.

```{r}
# Figure 1: Content Trust by CV and ID

ct_plot_data <- d_analysis %>%
  group_by(CV, ID) %>%
  summarise(
    n = n(),
    M = mean(CT, na.rm = TRUE),
    SD = sd(CT, na.rm = TRUE),
    SE = SD / sqrt(n),
    CI95 = qt(.975, df = n - 1) * SE,
    .groups = "drop"
  )

figure1_ct <- ggplot(
  ct_plot_data,
  aes(
    x = ID,
    y = M,
    group = CV,
    linetype = CV,
    shape = CV
  )
) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 3) +
  geom_errorbar(
    aes(
      ymin = M - CI95,
      ymax = M + CI95
    ),
    width = 0.08
  ) +
  labs(
    x = "Information Diagnosticity",
    y = "Mean Content Trust",
    linetype = "Commercial Visibility",
    shape = "Commercial Visibility"
  ) +
  ylim(1, 7) +
  theme_minimal()

figure1_ct

ggsave(
  filename = "../figures/figure1_content_trust.png",
  plot = figure1_ct,
  width = 7,
  height = 5,
  units = "in",
  dpi = 300
)
```
## 8.2 H3: Mediation via Persuasion Knowledge Awareness
```{r}
# Mediator model: effect of CV on PKA
pka_model <- lm(
  PKA ~ CV, 
  data = d_analysis
  )

summary(pka_model)

# Descriptive statistics for PKA by Commercial Visibility
pka_descriptives <- d_analysis %>%
  group_by(CV) %>%
  summarise(
    n = n(),
    M = mean(PKA, na.rm = TRUE),
    SD = sd(PKA, na.rm = TRUE),
    Median = median(PKA, na.rm = TRUE),
    .groups = "drop"
  )

pka_descriptives
```
```{r}
# Figure 2: Persuasion Knowledge Awareness by Commercial Visibility

figure2_pka <- ggplot(
  d_analysis,
  aes(
    x = CV,
    y = PKA
  )
) +
  geom_violin(
    trim = TRUE,
    alpha = 0.35
  ) +
  geom_boxplot(
    width = 0.14,
    outlier.shape = NA
  ) +
  geom_jitter(
    width = 0.08,
    height = 0,
    alpha = 0.22,
    size = 1
  ) +
  labs(
    x = "Commercial Visibility",
    y = "Persuasion Knowledge Awareness"
  ) +
  coord_cartesian(
    ylim = c(1, 7)
  ) +
  theme_minimal()

figure2_pka

ggsave(
  filename = "../figures/figure2_pka_by_cv.png",
  plot = figure2_pka,
  width = 7,
  height = 5,
  units = "in",
  dpi = 300
)
```
Figure 2 shows that PKA scores were concentrated toward the upper end of the scale in both conditions, with a modest upward shift under high Commercial Visibility.
```{r}
# Outcome model: effects of CV, ID and PKA on Content Trust
ct_mediation_model <- lm(
  CT ~ CV + ID + PKA,
  data = d_analysis
)

summary(ct_mediation_model)

# Outcome-model diagnostics
plot(
  ct_mediation_model,
  which = 1
)

plot(
  ct_mediation_model,
  which = 2
)

plot(
  ct_mediation_model,
  which = 4
)

# Original-sample indirect effect
a_h3 <- coef(pka_model)["CVHigh"]
b_h3 <- coef(ct_mediation_model)["PKA"]

h3_indirect_original <- a_h3 * b_h3

h3_indirect_original

# Bootstrap function for H3 indirect effect
bootstrap_h3 <- function(data) {
  
  sample_data <- data[
    sample(nrow(data), replace = TRUE),
  ]
  
  a_model <- lm(
    PKA ~ CV,
    data = sample_data
  )
  
  b_model <- lm(
    CT ~ CV + ID + PKA,
    data = sample_data
  )
  
  a <- coef(a_model)["CVHigh"]
  b <- coef(b_model)["PKA"]
  
  c(
    indirect_effect = a * b
  )
}

# Bootstrap indirect effect
set.seed(123)

bootstrap_h3_results <- replicate(
  5000,
  bootstrap_h3(d_analysis)
)

bootstrap_h3_results <- as.numeric(bootstrap_h3_results)

# Original-sample estimate with bootstrap 95% confidence interval
h3_bootstrap_summary <- data.frame(
  indirect_effect = h3_indirect_original,
  lower_95 = quantile(
    bootstrap_h3_results,
    0.025,
    na.rm = TRUE
  ),
  upper_95 = quantile(
    bootstrap_h3_results,
    0.975,
    na.rm = TRUE
  )
)

h3_bootstrap_summary
```
Diagnostic plots indicated no substantial systematic pattern in the residuals. The Q–Q plot showed close alignment across the central distribution with some deviation in the tails, while Cook’s distances indicated no observations with undue influence on the outcome model.

H3 was not supported. Persuasion Knowledge Awareness averaged 6.01 (SD = 1.24) under low CV and 6.34 (SD = 0.88) under high CV. As illustrated in Figure 2, PKA scores were shifted upward under high Commercial Visibility. Higher commercial visibility significantly increased PKA, B = 0.33, SE = 0.14, t(244) = 2.41, p = .017. However, PKA did not significantly predict Content Trust when CV and ID were included in the outcome model, B = 0.08, SE = 0.09, t(242) = 0.91, p = .363. The indirect effect of CV on Content Trust through PKA was not significant, B = 0.028, 95% CI [-0.029, 0.106].

## 8.3 H4: Moderated Mediation by Information Diagnosticity
```{r}
# Outcome model with PKA × ID interaction
ct_modmed_model <- lm(
  CT ~ CV + PKA_c * ID,
  data = d_analysis
)

summary(ct_modmed_model)

# Outcome-model diagnostics
plot(
  ct_modmed_model,
  which = 1
)

plot(
  ct_modmed_model,
  which = 2
)

plot(
  ct_modmed_model,
  which = 4
)

# Original-sample path estimates
a_h4 <- coef(pka_model)["CVHigh"]

b_low_h4 <- coef(
  ct_modmed_model
)["PKA_c"]

interaction_h4 <- coef(
  ct_modmed_model
)["PKA_c:IDHigh"]

b_high_h4 <- b_low_h4 + interaction_h4

# Original-sample conditional indirect effects
h4_indirect_low_original <- a_h4 * b_low_h4
h4_indirect_high_original <- a_h4 * b_high_h4

# Original-sample index of moderated mediation
h4_index_original <- a_h4 * interaction_h4

# Bootstrap function for H4 moderated mediation
bootstrap_h4 <- function(data) {
  
sample_data <- data[sample(nrow(data), replace = TRUE), ]
  
  # Re-centre PKA within each bootstrap sample
  sample_data <- sample_data %>%
    mutate(
      PKA_c = PKA - mean(PKA, na.rm = TRUE)
    )
  
  # a path: CV -> PKA
  a_model <- lm(PKA ~ CV, data = sample_data)
  
  # second-stage moderation model
  y_model <- lm(CT ~ CV + PKA_c * ID, data = sample_data)
  
  a <- coef(a_model)["CVHigh"]
  b_low <- coef(y_model)["PKA_c"]
  interaction <- coef(y_model)["PKA_c:IDHigh"]
  
  b_high <- b_low + interaction
  
  indirect_low <- a * b_low
  indirect_high <- a * b_high
  
  index_modmed <- a * interaction
  
  c(
    indirect_low = indirect_low,
    indirect_high = indirect_high,
    index_modmed = index_modmed
  )
}

set.seed(123)

bootstrap_h4_results <- replicate(
  5000,
  bootstrap_h4(d_analysis)
)

bootstrap_h4_results <- t(bootstrap_h4_results) %>%
  as.data.frame()

h4_bootstrap_summary <- data.frame(
  Effect = c(
    "Indirect effect at Low ID",
    "Indirect effect at High ID",
    "Index of moderated mediation"
  ),
  Estimate = c(
    h4_indirect_low_original,
    h4_indirect_high_original,
    h4_index_original
  ),
  Lower_95 = c(
    quantile(bootstrap_h4_results$indirect_low, 0.025, na.rm = TRUE),
    quantile(bootstrap_h4_results$indirect_high, 0.025, na.rm = TRUE),
    quantile(bootstrap_h4_results$index_modmed, 0.025, na.rm = TRUE)
  ),
  Upper_95 = c(
    quantile(bootstrap_h4_results$indirect_low, 0.975, na.rm = TRUE),
    quantile(bootstrap_h4_results$indirect_high, 0.975, na.rm = TRUE),
    quantile(bootstrap_h4_results$index_modmed, 0.975, na.rm = TRUE)
  )
)

h4_bootstrap_summary
```
Diagnostic inspection of the moderated mediation outcome model showed no substantial residual pattern or evidence of undue influence. Residuals followed the expected distribution closely across the central range, with some deviation in the tails.

H4 was not supported. The interaction between Persuasion Knowledge Awareness and Information Diagnosticity was not significant, B = −0.22, SE = 0.19, t(241) = −1.19, p = .235. The conditional indirect effect of CV on Content Trust through PKA was not significant at either low ID, B = 0.058, 95% CI [−0.004, 0.162], or high ID, B = −0.014, 95% CI [−0.131, 0.091]. The index of moderated mediation was also not significant, B = −0.073, 95% CI [−0.247, 0.038].

## 8.4 Secondary Outcome and Trust-Target Comparison

### 8.4.1 Platform Trust
```{r}
# Two-way ANOVA for Platform Trust
pt_model <- aov(
  PT ~ CV * ID, 
  data = d_analysis
  )

summary(pt_model)

# Platform Trust by experimental condition
pt_descriptives <- d_analysis %>%
  group_by(CV, ID) %>%
  summarise(
    n = n(),
    M = mean(PT),
    SD = sd(PT),
    .groups = "drop"
  )

pt_descriptives

# Effect sizes for Platform Trust ANOVA
eta_squared(
  pt_model,
  partial = TRUE
)

# Outcome-model diagnostics

qqnorm(residuals(pt_model))
qqline(residuals(pt_model))

fligner.test(
  PT ~ Condition,
  data = d_analysis
)
```
Residuals followed the expected distribution reasonably closely across the central range, with some deviation in the tails. The Fligner–Killeen test indicated no evidence of unequal variances across experimental conditions, χ²(3) = 3.13, p = .372.
As a secondary outcome, Platform Trust showed no significant main effect of Commercial Visibility, F(1, 242) = 1.82, p = .179, ηₚ² = .007. Information Diagnosticity had a significant positive effect on Platform Trust, F(1, 242) = 5.86, p = .016, ηₚ² = .02. The CV × ID interaction was not significant, F(1, 242) = 1.66, p = .199, ηₚ² = .007.

### 8.4.2 Comparison of Content Trust and Platform Trust
```{r}
# Reshape Content Trust and Platform Trust into long format
trust_long <- d_analysis %>%
  select(
    ResponseId,
    CV,
    ID,
    CT,
    PT
  ) %>%
  pivot_longer(
    cols = c(CT, PT),
    names_to = "TrustTarget",
    values_to = "Trust"
  ) %>%
  mutate(
    Participant = factor(ResponseId),
    TrustTarget = factor(
      TrustTarget,
      levels = c("CT", "PT"),
      labels = c(
        "Content Trust",
        "Platform Trust"
      )
    )
  )

# Mixed ANOVA: Trust Target is within-subject;
# CV and ID are between-subject factors
trust_target_model <- aov(
  Trust ~ TrustTarget * CV * ID +
    Error(Participant / TrustTarget),
  data = trust_long
)

summary(trust_target_model)

# Obtain partial eta-squared for trust-target interaction effects

trust_difference_model <- aov(
  I(CT - PT) ~ CV * ID,
  data = d_analysis
)

eta_squared(
  trust_difference_model,
  partial = TRUE
)
```
```{r}
# Figure 3: Content Trust and Platform Trust by Information Diagnosticity

trust_target_plot_data <- trust_long %>%
  group_by(ID, TrustTarget) %>%
  summarise(
    n = n(),
    M = mean(Trust, na.rm = TRUE),
    SD = sd(Trust, na.rm = TRUE),
    SE = SD / sqrt(n),
    CI95 = qt(.975, df = n - 1) * SE,
    .groups = "drop"
  )

figure3_trust_target <- ggplot(
  trust_target_plot_data,
  aes(
    x = ID,
    y = M,
    group = TrustTarget,
    linetype = TrustTarget,
    shape = TrustTarget
  )
) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 3) +
  geom_errorbar(
    aes(
      ymin = M - CI95,
      ymax = M + CI95
    ),
    width = 0.08
  ) +
  labs(
    x = "Information Diagnosticity",
    y = "Mean Trust",
    linetype = "Trust Target",
    shape = "Trust Target"
  ) +
  ylim(1, 7) +
  theme_minimal()

figure3_trust_target

ggsave(
  filename = "../figures/figure3_trust_target_by_id.png",
  plot = figure3_trust_target,
  width = 7,
  height = 5,
  units = "in",
  dpi = 300
)
```


A mixed ANOVA was conducted to directly compare the effects of Commercial Visibility and Information Diagnosticity across Content Trust and Platform Trust. There was a significant main effect of Trust Target, F(1, 242) = 16.17, p < .001, with overall Content Trust higher than Platform Trust. The Trust Target × CV interaction was not significant, F(1, 242) = 1.45, p = .230, ηₚ² = .006. In contrast, the Trust Target × ID interaction was significant, F(1, 242) = 7.77, p = .006, ηₚ² = .031, indicating that the positive effect of Information Diagnosticity differed across the two trust targets and was more pronounced for Content Trust. The three-way Trust Target × CV × ID interaction was not significant, F(1, 242) = 1.54, p = .216, ηₚ² = .006.

## 8.5 Hypothesis Summary
```{r}
hypothesis_table <- data.frame(
  Hypothesis = c("H1", "H2", "H3", "H4"),

  Prediction = c(
    "Higher CV will reduce Content Trust",
    "Higher ID will increase Content Trust",
    "CV will negatively affect Content Trust through PKA",
    "ID will moderate the indirect effect of CV on Content Trust through PKA, such that the negative indirect effect will be weaker when ID is high"
  ),

  `Key result` = c(
    "F(1, 242) = 0.09, p = .769, partial eta-squared < .001",
    "F(1, 242) = 23.60, p < .001, partial eta-squared = .09",
    "Indirect effect = 0.028, 95% CI [-0.029, 0.106]",
    "Index = -0.073, 95% CI [-0.247, 0.038]"
  ),

  `Key inference` = c(
    "Commercial visibility did not reduce Content Trust",
    "Information diagnosticity produced a positive effect on Content Trust",
    "CV increased PKA, but PKA did not mediate the effect on Content Trust",
    "Information diagnosticity did not moderate the indirect CV-PKA-Content Trust pathway"
  ),

  Conclusion = c(
    "Not supported",
    "Supported",
    "Not supported",
    "Not supported"
  ),

  check.names = FALSE
)

knitr::kable(
  hypothesis_table,
  caption = "Summary of Hypothesis Testing"
)
```
The trust-target comparison additionally showed that the positive effect of Information Diagnosticity was significantly stronger for Content Trust than for Platform Trust, whereas the effect of Commercial Visibility did not differ significantly between the two trust outcomes.