---
title: "social_commerce_content_perceptions_analysis"
author: "Eliana"
date: "2026-09-18"
output: word_document
---
# 0. Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
library(ggplot2)
library(tidyr)
library(psych)
library(effectsize)

options(scipen = 999)

d_raw <- read_csv('../data/01_raw_final_data.csv')
```
# 1. Research Questions and Hypotheses

## Main Research Question
How do commercial visibility and information diagnosticity influence Content Trust in creator-led social commerce?

## Sub-Research Question 1
Does persuasion knowledge awareness mediate the relationship between commercial visibility and Content Trust, and is this indirect relationship moderated by information diagnosticity?

## Sub-Research Question 2
Do commercial visibility and information diagnosticity affect Content Trust and Platform Trust differently?

## Hypotheses
H1: Higher CV will lead to lower Content Trust.

H2: Higher ID will lead to higher Content Trust.

H3: The negative effect of CV on Content Trust will be mediated by PKA.

H4: ID will moderate the indirect effect of CV on Content Trust via PKA, such that the negative indirect effect will be weaker when ID is high.

# 2. Raw Data Overview
```{r}
dim(d_raw)
names(d_raw)
d_raw %>%
  select(
    StartDate,
    Status,
    Progress,
    Finished,
    ResponseId,
    DistributionChannel,
    Condition
  ) %>%
  head(5)
```
